Incentivizing Exploration with Unbiased Histories

### 2019-03-25 COLT 2019 Submission/COLT rebuttal.txt

AnonReviewer1:
Q: Why does it matter if agent t' knows which observations agent t got if all agent t' does is essentially compute the sample mean from its observations?
A: First of all, they may not computing exactly sample means. Second, even if they are computing sample means, it matters to know if these are means from which sets of agents.

Q: I was surprised that the proof of Lemma 7 is not included
A: It could be proved using Chernoff bound and union bound. We will include it in the next version for completeness.

Q: Relatedly, in the proof of Lemma 18 when Lemma 7 is used to bound W^{a, s}_1, where does the middle inequality come from 
A: Sorry for the confusion. Lemma 7 is stated after applying union bound. And in Lemma 18, we are using Lemma 7 before the union bound step. We will make it more clear in the next version.

PC3: 
Q: I found the motivation behind the “unbiased subhistories” model not convincing: I don’t see why users, who wouldn’t trust minimal disclosure policies, should trust policies based on subhistories.  Even if the subhistories revealed to the agents are “unbiased”, the principal might still behave very differently (e.g., employ exploration) on the other rounds that are never disclosed.  Further, users do NOT know in advance whether they will be part of future subhistories.  Why would they react rationally in this setting?
A:

Q: The behaviour of agents in the model is also weird: the authors assume that the true mean reward of each arm is in the interval [1/3,2/3] (which is already suspicious), but then posit that agents make decisions according to empirical averages over revealed subhistories, which might fall out of this interval (granted, this happens only with a small probability, but precisely when exploration is needed).  So, it seems that agents in this model are not behaving very rationally.
A:

Q: The regret bounds in the paper are exponential in the number of arms K and other parameters of the problem.  Furthermore, the authors never mention this caveat explicitly in the paper, and only after browsing through the appendix (proof of Thm 5, with definitions from proof of Lem 4) did I realize that. (The authors do hint that their bounds are suboptimal w.r.t. K, but that is of course unsatisfactory.)
A:

AnonReviewer2: 
Q: In "Our scope" you assume that the info-graph is common knowledge. Do you mean that it is known by the agents? If so, where do they use it and is that reasonable to assume?
A:

Q: The authors claim that Assumption 1 is "much more permissive" than just assuming that the agents maximize their empirical averages. It seems a bit of an overstatement. Pulling each arm at least N_est ensures that the estimate used by the agents is at most 1/256N the empirical everage, where N is the number of pulls of the chosen arm up to the current round. It does not seem to change generality. If that is the case, can the authors elaborate on exactly why? 
A:

Q:In all the policies proposed in the paper, the constant L_K^FDP, used by the algorithm, depends on N_est (see proof of Lemma 4, page 15). This would imply that the algorithm knows N_est. It should be clearly stated as an assumption for the model.
A:

Q: In section 4 the authors set the number K of actions to 2. Is this without loss of generality? How do bounds depend on K if K is arbitrary?
A:

Q: Page 5, rewards are Bernoulli. Is this necessary? Do things work for arbitrary distributions on [0,1]?
A:

Q: Page 5, means are in [1/3, 2/3]. Is this necessary? Where do things break down if means are in [0,1]?
A:

### 2019-03-27 COLT 2019 Submission/COLT rebuttal.txt

============ Review 1 (AnonReviewer1) ===============

Thanks for the positive comments!

Q: Why does it matter if agent t' knows which observations agent t got if all agent t' does is essentially compute the sample mean from its observations?

A: Indeed, it doesn't matter once the behavioral model is fixed. But it helps to justify this model. As we explain (page 3, para 1), due to this "transitivity property" agent t' does not need to worry why agent t chose a particular action. Essentially, t' can just treat the subhistory as a set of data points, and not worry where they came from.

Q: I was surprised that the proof of Lemma 7 is not included

A: It has a fairly standard proof via Chernoff bounds. But good point, we will include it in a revision.

Q: Relatedly, in the proof of Lemma 18 when Lemma 7 is used to bound W^{a, s}_1, where does the middle inequality come from

A: Good catch, thanks! Lemma 7 is stated after applying union bound, and in Lemma 18, we are using Lemma 7 before the union bound step. We will fix this in a revision.

============== Review 2 (PC Member3) =================

Thanks for raising several important conceptual concerns. We believe these concerns can be easily addressed via a more careful discussion, as per the below. Note that a version of this discussion appeared in our response to STOC reviews, which we provided early on. Unfortunately, we didn't received STOC reviews until after the COLT submission deadline.

"why users, who wouldn’t trust minimal disclosure policies, should trust policies based on subhistories."

We argue that our mechanism requires substantially weaker trust/rationality assumptions compared to the minimal-disclosure policies.

There are several distinct issues here: that the agents (i) sufficiently understanding the announced policy, (ii) trusting the principal to want to implement it, (iii) trust him to actually implement it without bugs, and (iv) react to the policy in the way that we want.

Re (i), we only need an agent to understand that he is given an unbiased history -- doesn't matter which one  -- and it sees the entire message received by each agent in this subhistory. This is arguably pretty accessible, compared to a full-blown spec of a bandit algorithm.

Re (iii), faithfully revealing a subhistory is arguably easy, whereas debugging an actual bandit algorithm in a production-level system tends to be tricky.

Re (ii), a third party can, at least in principle, check collect subhistories from multiple agents and check them for consistency (e.g., that arms' average rewards are within the statistical deviations). Such checks appear virtually impossible for minimal-disclosure policies.

Re (iv), the agent should react to his subhistory as if it was just given a dataset, not thinking where this data came from. Whereas verifying that a minimal-disclosure policy is indeed incentive-compatible typically requires a sophisticated Bayesian reasoning.

"... the principal might still behave very differently ... on the other rounds that are never disclosed."

What happens outside of the revealed subhistory should not matter to the agent, because it does not affect the revealed subhistory.

"users do NOT know in advance whether they will be part of future subhistories."

It doesn't really matter for our model, but they do know: the info-flow graph is public.

"... mean reward of each arm is in the interval [1/3,2/3] (which is already suspicious), but ... agents make decisions according to empirical averages"

Indeed, our agents do not take into account that mean rewards lie in [1/3, 2/3]. Our justification is two-fold. First, we could posit incomplete information: agents simply do not know that mean rewards are restricted. Second, typical users are unlikely to implement a fully rational model. Following empirical averages appears much more natural. In particular, a realistic user should not estimate mean rewards as 1/3 if it keeps getting 0 rewards.

That the mean rewards lie in [1/3, 2/3] is a fairly mild assumption -- even for a bandit problem, let alone an incentivized exploration problem where NOTHING is known (without very strong trust/rationality assumptions).

Of course, [1/3, 2/3] can be replaced with [eps,1-eps] for any constant eps>0, which then propagates into the regret bounds.

"The regret bounds ... are exponential in [#arms]"

Indeed. However, such dependence is state-of-art in all prior work on incentivized exploration (see Mansour et al., 2015). We conjecture this is an inevitable "price of incentives". Note that this whole issue is irrelevant for two arms (which could be a paper on its own).

====== Review 3 (AnonReviewer2) ============

Thanks for raising several important conceptual concerns. We believe these concerns can be easily addressed via a more careful discussion, as per the below. Note that a version of this discussion appeared in our response to STOC reviews, which we provided early on. Unfortunately, we didn't received STOC reviews until after the COLT submission deadline.

"Overall, assumptions seem a bit heavy compared to the results obtained. "

A relevant comparison, in our opinion, is the state-of-art on incentivized exploration, where NOTHING was known without very strong trust/rationality assumptions.

"... you assume that the info-graph is common knowledge. Do you mean that it is known by the agents?"

Yes. It is reasonable, in the sense that the mechanism can "publish" whatever it wants. However, we don't need this assumption, neither formally nor to justify our model. We only need "unbiased history" with "transitivity".

"Assumption 1 is "much more permissive" than just assuming that the agents maximize their empirical averages."

We allow reward estimates to be within constant*ConfidenceRadius from the empirical averages, and we only make this assumption if N>N_est.

Put simply: rewards estimates are can differ from the empirical average, but not too much, and users reliably form such estimates only if they have sufficiently many samples.

"the algorithm knows N_est. It should be clearly stated." 
Agreed!

"In section 4 the authors set the number K of actions to 2." 
Section 4 is a graceful intro to the general result in Section 5. So, it posits K=2 for simplicity only.

"How do bounds depend on K if K is arbitrary?"

Our regret bounds are exponential in K (which we should make clearer). However, such dependence is state-of-art in all prior work on incentivized exploration (see Mansour et al., 2015). We conjecture this is an inevitable "price of incentives". Note that this whole issue is irrelevant for two arms (which could be a paper on its own).

Q: Page 5, rewards are Bernoulli. Is this necessary? Do things work for arbitrary distributions on [0,1]?

Bernoulli rewards is arguably the most important special case. However, this restriction is just for ease of exposition. Essentially, we only need {reward>3/4} and {reward<1/4} to happen with constant probability. 
%%% Jieming, is this true? I don't see why not.

"means are in [1/3, 2/3]. Is this necessary? Where do things break down  if means are in [0,1]?"

Yes, this seems essential for our analysis. 
%%% Jieming, can you concisely explain why?

Of course, [1/3, 2/3] can be replaced with [eps,1-eps] for any constant eps>0, which then propagates into the regret bounds.

Somewhat controversially, our behavioral model for agents does not take this fact into account. Our justification is two-fold. First, we could posit incomplete information: agents simply do not know that mean rewards are restricted. Second, typical users are unlikely to implement a fully rational model. Following empirical averages appears much more natural. In particular, a realistic user should not estimate mean rewards as 1/3 if it keeps getting 0 rewards.

### 2019-03-27 COLT 2019 Submission/COLT rebuttal.txt

Q: Page 5, rewards are Bernoulli. Is this necessary? Do things work for arbitrary distributions on [0,1]?

Bernoulli rewards is arguably the most important special case. However, this restriction is just for ease of exposition. Essentially, we only need {reward>3/4} and {reward<1/4} to happen with constant probability.

"means are in [1/3, 2/3]. Is this necessary? Where do things break down if means are in [0,1]?"

Yes, this seems essential for our analysis. When arms' means can get closer to 1, for example, let's say some arm has mean 1-1/T^{0.1}. Then in our solution, this arm will with high probability stop agents from exploring other arms with small initial estimates (e.g. 0.5) and better actual means (e.g. 1).

### 2019-04-15 intro.tex
king of self-citation
Revised to address reviewers' comments, as per our rebuttals.

This situation can be circumvented by a centralized algorithm that induces agents to take explorative actions, an idea called {\em incentivizing exploration}.  Such algorithms are often encountered in the form of recommendations and are quite common in practice.  Many online websites, like Amazon, Reddit, Yelp, and Tripadvisor, among many others, use recommendation policies of some sort to help users navigate their offerings.
%
One way recommendation policies induce exploration is to introduce payments, \eg~\cite{Frazier-ec14,Kempe-colt18}. For example, the recommendation system of an online retailer might offer coupons to agents for trying certain products.  When payments are financially or technologically infeasible, another alternative is to rely on information asymmetry, \eg~\cite{Kremer-JPE14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17}.
Here the idea is that the centralized algorithm, often called a {\em disclosure policy}, can choose to selectively release information about the past actions and rewards to the agents in the form of a {\em message}.  For example, the recommendation system of an online retailer might disclose past reviews or product rankings to the agents.  Importantly, agents can not directly observe the past, but only learn about it through this message.  The agent then chooses an action, using the content of the message as input.

\xhdr{Our scope.} Prior work on incentivizing exploration, with or without monetary incentives, achieves much progress (more on this in ``related work"), but relies heavily on the standard assumptions of Bayesian rationality and the ``power to commit" (\ie users trust that the principal actually implements the policy that it claims to implement). However, these assumptions appear quite problematic in the context of recommendation systems of actual online websites such as those mentioned above. In particular, much of the prior work suggests disclosure policies that merely recommend an action to each agent, without any other supporting information, and moreover recommend exploratory actions to some randomly selected users. This works out extremely well in theory, but it is very unclear whether users would even know some complicated policy of the principal, let alone trust the principal to implement the stated policy. Even if they do know the policy and trust that it was implemented as claimed, it's unclear whether users would react to it rationally.
%
Several issues are in play: to wit, whether the principal intentionally uses a different disclosure policy than the claimed one (\eg because its incentives are not quite aligned with the users'), whether the principal correctly implements the policy that it wants to implement, whether the users trust the principal to make correct inferences on their behalf, and whether they find it acceptable that they may be singled out for exploration. Furthermore, regardless of how the users react to such disclosure policies, they may prefer not to be subjected to them, and leave the system.

We strive to design disclosure policies which mitigate these issues and (still) incentivize a good balance between exploration and exploitation. While some assumptions on human behavior are unavoidable, we are looking for a class of disclosure policies for which we can make plausible behavioral assumptions. Then we arrive at a concrete mathematical problem: design policies from this class so as to optimize performance, \ie  the induced explore-exploit tradeoff. Our goal in terms of performance is to approach the performance of the social planner.

\xhdr{Our model.}
For the sake of intuition, let us revisit the \emph{full-disclosure policy} that reveals the full history of observations from the previous users. We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it. Unfortunately, the full-disclosure policy is not good for our purposes, essentially because we expect users to \emph{exploit} rather than \emph{explore}. However, what if a disclosure policy reveals the outcomes for every tenth agent, rather than the outcomes for all agents? We posit that users would trust such policy, too. Given a large volume of data, we posit that users would not be too unhappy with having access to only a fraction this data. A crucial aspect of our intuition here is that the ``subhistory" revealed to a given user comes from a subset of previous users that is chosen in advance, without looking at what happens during the execution. In particular, the subhistory is not ``biased", in the sense that the disclosure policy cannot subsample the observations in favor of a particular action.

With this intuition in mind, we define the class of \emph{unbiased-subhistory policies}: disclosure policies that reveal, to each arriving agent $t$, a subhistory  consisting of the outcomes for a subset $S_t$ of previous agents, where $S_t$ is chosen ahead of time. Further, we impose a transitivity property: if $t' \in S_t$, for some previous agent $t'$, then $S_{t'}\subset S_t$. So, agent $t$ has all information that agent $t'$ had at the time she chose her action. In particular, agent $t$ does not need to second-guess which message has caused agent $t'$ to make choose that action.

Following much of the prior work on incentivizing exploration, we do not attempt to model heterogenous agent preferences and non-stationarity. Formally, we assume that the expected reward of taking a given action $a$, denoted $\mu_a$, is the same for all agents, and does not change over time. Then the crucial parameter of interest, for a given action $a$, are the number of samples $N_a$ and the empirical mean reward $\bar{\mu}_a$ in the observed subhistory. We consider a flexible model of agent response: for each action $a$ an agent forms an estimate $\hat{\mu}_a$ of the mean reward $\mu_a$, roughly following $\bar{\mu}_a$ but taking into account the uncertainty due to a small number of samples, and chooses an action with a largest reward estimate. We allow the reward estimates to be arbitrary otherwise, and not known to the principal.

@@

\xhdr{Our results and discussion.}
Our main result is a transitive, unbiased-subhistory policy which attains near-optimal $\tilde{O}(\sqrt{T})$ regret rate for a constant number of actions. This policy also obtains the optimal instance-dependent regret rate
    $\tilde{O}(\tfrac{1}{\Delta})$
for problem instances with gap $\Delta$, without knowing the $\Delta$ in advance. In particular, we match the regret rate achieved for incentivizing exploration with unrestricted disclosure policies \cite{ICexploration-ec15-working}.

@@

>>>>

This situation can be circumvented by a centralized algorithm that induces agents to take explorative actions, an idea called {\em incentivizing exploration}.  Such algorithms are often encountered in the form of recommendations and are quite common in practice.  Many online websites, like Amazon, Reddit, Yelp, and Tripadvisor, among many others, use recommendation policies of some sort to help users navigate their offerings.
%
One way recommendation policies induce exploration is to introduce payments, \eg~\cite{Frazier-ec14,KKMPRVW17,Kempe-colt18}. For example, the recommendation system of an online retailer might offer coupons to agents for trying certain products.  When payments are financially or technologically infeasible, another alternative is to rely on information asymmetry, \eg~\cite{Kremer-JPE14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17}.
Here the idea is that the centralized algorithm, often called a {\em disclosure policy}, can choose to selectively release information about the past actions and rewards to the agents in the form of a {\em message}.  For example, the recommendation system of an online retailer might disclose past reviews or product rankings to the agents.  Importantly, agents can not directly observe the past, but only learn about it through this message.  The agent then chooses an action, using the content of the message as input.

\xhdr{Our scope.} Prior work on incentivizing exploration, with or without monetary incentives, achieves much progress (more on this in ``related work"), but relies heavily on the standard assumptions of Bayesian rationality and the ``power to commit" (\ie users trust that the principal actually implements the policy that it claims to implement). However, these assumptions appear quite problematic in the context of recommendation systems of actual online websites such as those mentioned above. In particular, much of the prior work suggests disclosure policies that merely recommend an action to each user, without any other supporting information, and moreover recommend exploratory actions to some randomly selected users. This works out extremely well in theory, but it is very unclear whether users would even know some complicated policy of the principal, let alone trust the principal to implement the stated policy. Even if they do know the policy and trust that it was implemented as claimed, it's unclear whether users would react to it rationally.
%
Several issues are in play: to wit, whether the principal intentionally uses a different disclosure policy than the claimed one (\eg because its incentives are not quite aligned with the users'), whether the principal correctly implements the policy that it wants to implement,%
\footnote{\asedit{Large-scale systems that implement bandit algorithms can be notoriously difficult to debug \cite{DS-arxiv}.}}
 whether the users trust the principal to make correct inferences on their behalf, and whether they find it acceptable that they may be singled out for exploration. Regardless of how the users react to such disclosure policies, they may prefer not to be subjected to them, and leave the system.

We strive to design disclosure policies which mitigate these issues and (still) incentivize a good balance between exploration and exploitation. While some assumptions on human behavior are unavoidable, we are looking for a class of disclosure policies for which \asedit{they are (more) plausible}. Then we arrive at a concrete mathematical problem: design policies from this class so as to optimize performance, \ie  the induced explore-exploit tradeoff. Our goal in terms of performance is to approach the performance of the social planner.

\xhdr{Our model.}
For the sake of intuition, let us revisit the \emph{full-disclosure policy} that reveals the full history of observations from the previous users. We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it. Unfortunately, the full-disclosure policy is not good for our purposes, essentially because we expect users to \emph{exploit} rather than \emph{explore}. However, what if a disclosure policy reveals the outcomes for every tenth user, rather than the outcomes for all users? We posit that users would trust such policy, too. Given a large volume of data, users would not be too unhappy with having access to only a fraction this data.

A crucial aspect of our intuition here is that the ``subhistory" revealed to a given user comes from a subset of previous users that is chosen in advance, without looking at what happens during the execution. In particular, the subhistory is not ``biased", in the sense that the disclosure policy cannot subsample the observations so as to make a particular action look good. \asedit{(If a subhistory is subsampled in favor of some action, revealing is essentially no better than just issuing a recommendation without any supporting evidence.)}
With this intuition in mind, we define the class of \emph{unbiased-subhistory policies}: disclosure policies that reveal, to each arriving agent $t$, a subhistory  consisting of the outcomes for a subset $S_t$ of previous agents, where $S_t$ is chosen ahead of time. 
\asedit{(From here on, we will use ``users" and ``agents" interchangeably.)}

Further, we impose a transitivity property: if $t' \in S_t$, for some previous agent $t'$, then $S_{t'}\subset S_t$. In words, agent $t$ has all information that agent $t'$ had at the time she chose her action. \asedit{Agent $t$ does not need to second-guess which message has caused agent $t'$ to choose that action, since such second-guessing cannot possibly yield any additional information. Essentially, agent $t$ can treat the subhistory as a set of data points collected by an algorithm, and not worry how these data points has been affected by other agents' choices.}

Following much of the prior work on incentivizing exploration, we do not attempt to model heterogenous agent preferences and non-stationarity. We assume that the expected reward of taking a given action $a$, denoted $\mu_a$, is the same for all agents, and does not change over time.

We consider a flexible model of agent response. For each action $a$, the crucial statistics are the number of samples $N_a$ and the empirical mean reward $\bar{\mu}_a$ in the observed subhistory. An agent forms an estimate $\hat{\mu}_a$ of the mean reward $\mu_a$, roughly following $\bar{\mu}_a$ but taking into account the uncertainty due to a small number of samples, and chooses an action with a largest reward estimate. We allow the reward estimates to be arbitrary otherwise. 
\asedit{The way they depend on the observed statistics may differ from one agent to another. This dependence, as well as the statistics and the reward estimates, are not known to the principal. We make no assumptions whatsoever unless an agent has sufficiently many samples from a given arm.}

\asedit{Our model of agent response is justified by the assumption of unbiased, transitive subhistory. This assumption is no longer needed once the model is assumed. The model is justified regardless of what the agents know about the subsets $(S_{t}: t\in [T])$. In particular, we could posit that these subsets are common knowledge, or that the agents do not know them, not even their own subset.}

@@

\xhdr{Our results and techniques.}
Our main result is a transitive, unbiased-subhistory policy which attains near-optimal $\tilde{O}(\sqrt{T})$ regret rate for a constant number of actions. This policy also obtains the optimal instance-dependent regret rate
    $\tilde{O}(\tfrac{1}{\Delta})$
for problem instances with gap $\Delta$, without knowing the $\Delta$ in advance. In particular, we match the best possible regret rates for the multi-armed bandit problem (same as the prior work on unrestricted disclosure policies \cite{ICexploration-ec15-working}). 
\asedit{Each agent $t$ sees a substantial fraction of history available at time $t$: namely, our policy reveals a subhistory of
size at least $\Omega( t/\polylog(T))$.
Our regret bounds scale exponentially in the number of actions; this dependence is grossly suboptimal for multi-armed bandits, but matches the state-of-art for unrestricted disclosure policies \cite{ICexploration-ec15-working}, and is conjectured to be unavoidable for incentivized exploration.}

@@

\ascomment{The following xhdr is new}

\xhdr{Discussion.}
We argue that our subhistory-based policies require substantially weaker trust and rationality assumptions compared to the minimal-disclosure policies in prior work. There are several distinct issues here:

\begin{itemize}

\item \emph{Whether agents sufficiently understand the announced policy.} We only need an agent to understand that he is given some unbiased history. It does not matter what is the subset of rounds and how it is related to the other agents' subsets. This is arguably quite comprehensible, compared to a full-blown spec of a bandit algorithm.

\item \emph{Whether agents trust the principal's intent to implement the stated policy.} A third party can, at least in principle, collect subhistories from multiple agents and check them for consistency (e.g., that arms' average rewards are within the statistical deviations). This should create incentives for the principal not to manipulate the policy. Note that similar checks appear virtually impossible for minimal-disclosure policies.

\item \emph{Whether agents trust the principal to implement the stated policy without bugs.}
    Faithfully revealing a subhistory is arguably easy, whereas (as noted above) debugging an actual bandit algorithm in a large-scale production-level system tends to be quite complicated.

\item \emph{Whether agents react to the policy in a way that we assume.}
In our framework, an agent should react to the subhistory as if it was a set of data points collected by an algorithm, free from other agents' influence. The system can provide summary statistics, so that agents would not need to actually look at the raw data.%
\footnote{Trusting the summary statistics is a relatively minor issue, one where "cheating" can, in principle, be easily verified.}
Whereas verifying that a minimal-disclosure policy is indeed incentive-compatible typically requires a sophisticated Bayesian reasoning.

\end{itemize}

Even though we are not showing full histories, even a small fraction of history would realistically contain a large number of datapoints. Besides, a user usually looks at a small sample of reviews. In our case, one could say that these reviews are just pre-selected by the algorithm (in an ``unbiased" and ``transitive" way, as explained above).

For the sake of the analysis, we assume that the mean rewards lie in the interval
    $[\nicefrac{1}{3}, \nicefrac{2}{3}]$,
whereas the agents' response model does not take this fact into account.% 
\footnote{Of course, the $[\nicefrac{1}{3}, \nicefrac{2}{3}]$ restriction can be replaced with $[\eps,1-\eps]$ for any given global constant $\eps>0$ (which would then propagate into the regret bounds).}
Our justification is two-fold. First, agents may operate under incomplete information: they simply do not know that mean rewards are restricted. Second, typical users of a recommendation system are unlikely to be fully rational (whether Bayesian or not). Following empirical averages appears much more natural. In particular, a realistic user should not estimate mean rewards as $\nicefrac{1}{3}$ if it keeps getting $0$ rewards.

On a final note, we emphasize that we provide the first result on incentivized exploration that does not rely on the strong assumptions of trust and rationality.
